The Markov Link Method: a nonparametric approach to combine observations from multiple experiments

### 2018-08-16 paper/paper.tex
Gave some context for size of projection distance

In practice, we were not able to find a way to compute these objects exactly.  Given samples from the posterior distribution $\mathbb{P}(\plx,\ply| \DX,\DY,\Gamma(\plx,\ply)=0)$, it would be straightforward to get good estimates.  As seen in Appendix \ref{sec:optproblems}, it is straightforward to compute $\pxy_{\mathrm{lo}},\pxy_{\mathrm{hi}},\hat \pxy$ from samples of $\plx,\ply$, so we could use use monte-carlo approximations for our objects of interest.  Unfortunately, it seems difficult to obtain samples from this posterior distribution.   Common approaches to this type of problem involve Markov-Chain Monte Carlo and Variational Inference, but we were unable to make these approaches work in practice.  It seems nontrivial to work with the condition $\Gamma(p,h)=0$ that formalizes the \MLM{} assumption.  We instead take a somewhat na\"ive approach.  We start by drawing samples according to
\[
F,H ~ \sim \mathbb{P}(\plx,\ply | \DX,\DY)
\]
This can be achieved exactly, using the the conjugacy between our prior and the Multinomial distribution.  Notice that these samples do not incorporate our knowledge of the \MLM{} assumption, insofar as they are not conditioned on the event $\Gamma(\plx,\ply)=0$.  To approximately remedy this, we define $\tilde H$ as the solution of $\min_{h'}D(H|h')$, subject to the constraint that $\Gamma(F,h')=0$.  Optimization details can be found in Appendix \ref{sec:optproblems}.  We use the pair $F,\tilde H$ as \emph{approximate} samples for the distribution $\mathbb{P}(\plx,\ply| \DX,\DY,\Gamma(\plx,\ply)=0)$.  We can repeat this process to produce many samples of $(F,\tilde H)$ and use those samples to produce approximate monte-carlo estimates for $\hat \pxy(y|x),C_{x,y}$.  We asymptotically expect that $F,H$ will nearly satisfy the MLM assumption in any case, so this approximation should not make a large difference.  However, we caution that the exact implications of the approximation are difficult to reason about.   In any case, it is a practical solution to a difficult problem.

>>>>

In practice, we were not able to find a way to compute these objects exactly.  Given samples from the posterior distribution $\mathbb{P}(\plx,\ply| \DX,\DY,\Gamma(\plx,\ply)=0)$, it would be straightforward to get good estimates.  As seen in Appendix \ref{sec:optproblems}, it is straightforward to compute $\pxy_{\mathrm{lo}},\pxy_{\mathrm{hi}},\hat \pxy$ from samples of $\plx,\ply$, so we could use use monte-carlo approximations for our objects of interest.  Unfortunately, it seems difficult to obtain samples from this posterior distribution.   Common approaches to this type of problem involve Markov-Chain Monte Carlo and Variational Inference, but we were unable to make these approaches work in practice.  It seems nontrivial to work with the condition $\Gamma(p,h)=0$ that formalizes the \MLM{} assumption.  We instead take a somewhat na\"ive approach.  We start by drawing samples according to
\[
F,H ~ \sim \mathbb{P}(\plx,\ply | \DX,\DY)
\]
This can be achieved exactly, using the the conjugacy between our prior and the Multinomial distribution.  Notice that these samples do not incorporate our knowledge of the \MLM{} assumption, insofar as they are not conditioned on the event $\Gamma(\plx,\ply)=0$.  To approximately remedy this, we define $\tilde H$ as the solution of $\min_{h'}D(H|h')$, subject to the constraint that $\Gamma(F,h')=0$.  Optimization details can be found in Appendix \ref{sec:optproblems}.  We use the pair $F,\tilde H$ as \emph{approximate} samples for the distribution $\mathbb{P}(\plx,\ply| \DX,\DY,\Gamma(\plx,\ply)=0)$.  We can repeat this process to produce many samples of $(F,\tilde H)$ and use those samples to produce approximate monte-carlo estimates for $\hat \pxy(y|x),C_{x,y}$.  We asymptotically expect that $F,H$ will nearly satisfy the MLM assumption in any case, so this approximation should not make a large difference.  For example, on the Allen Institute data we found that the total variation distance between $H(\cdot|\ell)$ and $\tilde H(\cdot|\ell)$ was about 15\% (averaging over all selection procedures $\ell$ and various samples of $H$).  For comparison, this is about three times smaller than the average total variation distance between $H(\cdot|\ell)$ and $H(\cdot|\ell')$ for a randomly selected pair of selection procedures $(\ell,\ell')$, which averages out to around 50\%.   In any case, it is a practical solution to a difficult problem.
